Translation of B Implementations to the LLVM: Specification

### 2014-04-04 DOCUMENTATION/specification.tex
Organising the position of derived types section.

@@

@@

\include{DerivedTypes}

>>>>

\include{derivedTypes}

@@

\paragraph{Becomes equal instructions} \textcolor{blue}{ must evaluate the
 target and the source of the assignment, and then copy the result of the 
latter in the former, using the LLVM instruction \llvm{store}. The evaluation 
of the target is defined with $\trad{}{lvalue}$, which yields the corresponding 
LLVM source code $l$ and the variable $p$ containing the assigned location. The 
evaluation of the source yields the corresponding code $r$, the variable $v$ 
holding the result, and its type $t$. }

\begin{align*}
\begin{split}
  \trad{a}{\B{Beq}} \isdef
  & \LET l \sep p \sep t'= \trad{a.lhs}{lvalue} \AND r \sep v \sep t = \trad{a.rhs}{\B{Exp}} \IN \\
  & \llvm{"\PH{l}} \\
  & \llvm{\PH{r}} \\
  & \llvm{store \PH{t} \PH{v}, \PH{t'} \PH{p} \nl"}
\end{split}
\end{align*}

The rule lvalue is:
\begin{align*}
\lefteqn{\trad{n}{lvalue} \isdef} \\
& \LET t = \llvm{"\PH{\trad{\B{n.type}}{Type}}"} \IN \\
& \quad \IF \mbox{\B{n} is a local variable} \THEN \llvm{""} \sep \local(\B{n}) \sep t \\
& \quad \IF \mbox{\B{n} is an ArrayItem} \THEN  \trad{n}{ArrayItem} \\
& \quad \IF \mbox{\B{n} is a RecField} \THEN  \trad{n}{RecField} \\
& \quad \ELSE \LET v = \variable \IN \\
& \quad \quad \llvm{"\PH{v} = getelementptr \PH{\state(\B{n.root})}* \%self\$,} \\
& \quad \quad \quad \llvm{i32 0, i32 \PH{\idx(\B{n})} \nl"} \sep v \sep t
\end{align*}

\textcolor{blue}{ The expressions have elements represented by pointers that need a special 
care. The attributions between these elements are made  directly by the memory 
address.  However, the expression resolution are made by parts, where the 
partial results are stored to temporary variables. Therefore, the expression 
resolution with pointers needs an additional instruction $LOAD$ for store the 
partial results. This translation is represented by $ValueItem$.}

\begin{align*}
\begin{split}
  \trad{n}{\B{ValueItem}} \isdef \\
   & \LET \ell = \lbl  \IN\\
   & \IF \B{n} \mbox{ is \B{RecField}} \THEN p' \sep v' \sep t' = \trad{\B{n}}{\B{RecField}} \\
   & \ELSIF \B{n} \mbox{ is \B{ArrayItem}} \THEN p' \sep v' \sep t' = \trad{\B{n}}{\B{ArrayItem}} \\
   & \llvm{"\PH{p'} \PH{\ell}  = load  \PH{t'}* \PH{v'} \nl"} \\
   & \sep  \ell  \sep t'\\
\end{split}
\end{align*}

@@
